\documentclass[12pt]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{ulem}
\usepackage{array}
\usepackage{enumitem}

\begin{document}

\begin{center}
\textbf{Sino Bright School Chongqing}

\vspace{0.5cm}
\Large\textbf{MONTHLY EXAM, 2024-2025 T2}

\vspace{1cm}
\begin{tabular}{ll}
\textbf{Subject:} & Further Math \\
\textbf{Date:} & May 2025 \\
\textbf{Time:} & 90 minutes \\
\textbf{Teacher Responsible:} & Shi Feng \\
\end{tabular}
\end{center}

\vspace{1cm}
\noindent\textbf{IMPORTANT: Read together before beginning the exam.}

\smallskip
\noindent Students must complete the assessments to the best of their ability. Any students found cheating during an exam will be given a zero and referred to the Principal for further disciplinary measures. Cheating is a serious offense.

\medskip
\noindent "Cheating" may include any of the following:
\begin{itemize}[leftmargin=*]
    \item Having course papers, notes, unapproved data sheets or other course-related materials in the exam room without the express permission of the subject class teacher in charge of the exam.
    
    \item Using or even having a cellphone or other electronic device in the exam room without the express permission of the subject class teacher in charge of the exam.
    
    \item Attempting to communicate, either verbally or non-verbally with other students during the exam.
    
    \item Having exam-related materials prior to the writing of the exam.
\end{itemize}

\vspace{0.5cm}
\noindent\textbf{Mark Breakdown:}
\begin{center}
\begin{tabular}{|l|r|}
\hline
Part 1: Multiple Choice Questions & $5 \times 10$ \\ \hline 
Part 2: Short Answer Questions & $5 \times 4$ \\ \hline
Part 3: Long Answer Questions & $2 \times 15$ \\ \hline
Total Score & 100 \\ \hline
\end{tabular}
\end{center}

\vspace{1cm}
\noindent\textbf{Student Name:} \uline{\hspace{8cm}}

\vspace{0.5cm}
\noindent\textbf{Score:} \uline{\hspace{8cm}}

\vspace{0.5cm}
\noindent\textbf{Special Instructions/Materials Allowed:}
\begin{itemize}[leftmargin=*]
    \item Pen
\end{itemize}

\end{document}